Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-02-01 paperMSR.tex

\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}

\begin{figure}[ht]
\centering
\includegraphics[height=2.5cm]{manyprevious.png}
\caption{Previous commits: \textit{e7be0a988} (left) and \textit{e5296c1da} (right).}
\label{fig:manyprevious}       % Give a unique label
\end{figure}

@@

As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause. We were unable to decide in 42 cases, as only lines had been added or due to our limited knowleadge about the code. \grex{Gema, puedes poner un ejemplo de estas dos cosas? Uno de solo added lines y otro de limited knowledge. Si el ejemplo es verdadero, mejor.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.

\begin{table}[htb]
\begin{center}
\begin{tabular}{lrr}
\toprule[0.3mm]
  & \multicolumn{1}{c}{Before} & \multicolumn{1}{c}{After} \\
  & \multicolumn{1}{c}{Deleting Noise} & \multicolumn{1}{c}{Deleting Noise} \\\hline
{Cause} & (152) 44\% & (152) 49\% \\[0ex]
{Not Cause} & (154) 44\% & (114) 37\% \\[0ex]
{Undecided} & (42) 12\% & (42) 14\% \\[0ex]
\bottomrule[0.3mm]
\end{tabular}
\caption{Number of times (and percentage) where the previous commit is the cause, not the cause or could not be classified, before and after deleting noise.}
\label{tab:responsability}
\end{center}
\end{table}

>>>>

\grex{No estan mal las descripciones superiores en la figura~\ref{fig:manyprevious} que dice ``After Fix Bug'' y ``Fix-inducing (Before fix bug)''?}
\gema{creo que no, la de la izquierda es despues de que se arreglara el error, y la de la derecha es en el momento en que se introdujo el error}
\begin{figure}[ht]
\centering
\includegraphics[height=2.5cm]{manyprevious.png}
\caption{Previous commits: \textit{e7be0a988} (left) and \textit{e5296c1da} (right).}
\label{fig:manyprevious}       % Give a unique label
\end{figure}

@@

As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause. We were unable to decide in 42 cases, as only lines had been added \ref{fig:8} and we cannot be able to know which previous commit could be the one that forgot added this lines, or due to our limited knowleadge about the code \ref{fig:9}. \grex{Gema, puedes poner un ejemplo de estas dos cosas? Uno de solo added lines y otro de limited knowledge. Si el ejemplo es verdadero, mejor.}\gema{Me faltaria el ejempli de limited knowledge, cuando encuentre uno bueno lo anado}
We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.
\begin{figure}[ht]
\centering
\includegraphics[height=1cm]{addedlines.png}
\label{fig:8}       % Give a unique label
\caption{Example of added lines where we are unable to decide which previous commit caused the bug}
%52919
\end{figure}

%\begin{figure}[ht]
%\centering
%\includegraphics[height=2cm]{unknown.png}
%\label{fig:9}       % Give a unique label
%\caption{Example of unknowleadge where we are unable to decide which previous commit caused the bug }
%\end{figure}
\begin{table}[htb]
\begin{center}
\begin{tabular}{lrr}
\toprule[0.3mm]
  & \multicolumn{1}{c}{Before} & \multicolumn{1}{c}{After} \\
  & \multicolumn{1}{c}{Deleting Noise} & \multicolumn{1}{c}{Deleting Noise} \\\hline
{Cause} & (152) 44\% & (152) 49\% \\[0ex]
{Not Cause} & (154) 44\% & (114) 37\% \\[0ex]
{Undecided} & (42) 12\% & (42) 14\% \\[0ex]
\bottomrule[0.3mm]
\end{tabular}
\caption{Number of times (and percentage) where the previous commit is the cause, not the cause or could not be classified, before and after deleting noise.}
\label{tab:responsability}
\end{center}
\end{table}
